Longitudinal Principal Manifold Estimation

### 2024-02-12 paper/main.tex
address latex warnings

\usepackage[
backend=biber,
style=authoryear,
url=false,
isbn=false,
date=year,
doi=false,
pmid=false,
urldate=false
]{biblatex}

@@

\begin{figure}[ht]
  \centering
  \subfloat[\centering Data]{{\label{fig:lpme_step1} \includegraphics[width=8cm]{sim_case1_plot2}}}%
  \hfill
  \subfloat[\centering Step 1: Sample Size Reduction]{{\label{fig:lpme_step2} \includegraphics[width=8cm]{lpme_data_reduction}}}
  \vfill
  \subfloat[\centering Step 2: Initialization]{{\label{fig:lpme_step3} \includegraphics[width=8cm]{lpme_initialization}}}
  \hfill
  \subfloat[\centering Steps 3 and 4: Fitting and Tuning]{{\label{fig:lpme_step4} \includegraphics[width=8cm]{lpme_fitting}}}
  \caption{LPME Algorithm Steps. In (a) we show the original data cloud, in (b) we show the sample size reduction step, where the red points indicate the representative data to be used for the next steps of the algorithm, (c) shows the fitted time specific curves, the blue surface in (d) shows the estimated smooth surface. }
  \label{fig:lpme_steps}
\end{figure}

@@

Figure \ref{fig:lhipp_cross_section} depicts cross sections of the observed hippocampus surface and the estimated surface obtained using LPME and PME at each individual time point. These cross sections illustrate the differences between the estimates reached by the PME and LPME algorithms, with the LPME-based estimate being generally less responsive to changes in the shape and orientation of the hippocampus between time points. This figure reiterates that both the PME and LPME algorithms are unable to capture the distinctive sharp curve in the structure at the upper-left corner of each of the plots. Additionally, we see that, along the upper-right edge of the surface, there is a spot where the estimated manifold intersects with itself. This is present for both the PME and LPME estimates, but appears to be more prevalent when using LPME. Notably, it also appears that the boundaries of the LPME-estimated surface tend to fall inside the boundaries of the PME-estimated surface, particularly at locations with the highest levels of curvature.

>>>>

\usepackage[
backend=biber,
style=authoryear,
url=false,
isbn=false,
date=year,
doi=false
]{biblatex}

@@

\begin{figure}[ht]
  \centering
  \subfloat[\centering Data]{\label{fig:lpme_step1} \includegraphics[width=8cm]{sim_case1_plot2}}%
  \hfill
  \subfloat[\centering Step 1: Sample Size Reduction]{\label{fig:lpme_step2} \includegraphics[width=8cm]{lpme_data_reduction}}
  \vfill
  \subfloat[\centering Step 2: Initialization]{\label{fig:lpme_step3} \includegraphics[width=8cm]{lpme_initialization}}
  \hfill
  \subfloat[\centering Steps 3 and 4: Fitting and Tuning]{\label{fig:lpme_step4} \includegraphics[width=8cm]{lpme_fitting}}
  \caption{LPME Algorithm Steps. In (a) we show the original data cloud, in (b) we show the sample size reduction step, where the red points indicate the representative data to be used for the next steps of the algorithm, (c) shows the fitted time specific curves, the blue surface in (d) shows the estimated smooth surface. }
  \label{fig:lpme_steps}
\end{figure}

@@

Figure \ref{fig:lhipp_cross_sections} depicts cross sections of the observed hippocampus surface and the estimated surface obtained using LPME and PME at each individual time point. These cross sections illustrate the differences between the estimates reached by the PME and LPME algorithms, with the LPME-based estimate being generally less responsive to changes in the shape and orientation of the hippocampus between time points. This figure reiterates that both the PME and LPME algorithms are unable to capture the distinctive sharp curve in the structure at the upper-left corner of each of the plots. Additionally, we see that, along the upper-right edge of the surface, there is a spot where the estimated manifold intersects with itself. This is present for both the PME and LPME estimates, but appears to be more prevalent when using LPME. Notably, it also appears that the boundaries of the LPME-estimated surface tend to fall inside the boundaries of the PME-estimated surface, particularly at locations with the highest levels of curvature.
